### 2019-07-10 2-Chapters/5-Chapter/chapter5.tex
Last pass with http://emccabedj.ucc.asn.au/checktex.html

\paragraph{Performance of our proposals for a wrong value of $M$.}
\label{par:5:usingWrongValueofM}
%
We can start by asking whether the most efficient algorithm, \MCTopM-\klUCB, is still efficient if it uses a value $M'$ different than the real number of players $M$.
Even though we did not include numerical simulations for this case in Section~\ref{sec:5:experiments} above, we did some tests, which confirmed two disappointing results that were also proven analytically.
First, the three algorithms (\RhoRand, \RandTopM{} and \MCTopM) give linear regret if they are using a value $M'$ strictly smaller than $M$ (and if $\mu^*_{M-1} > \mu^*_M$), as players will converge to play about $T-\bigO{\log(T)}$ times the $M-1$ best arms, leading to at least one collision most of the time, and thus a linear regret.
Second, if the $M$ players falsely use a value $M' > M$, then there is also a certain (fixed) probability to achieve a linear regret. Indeed, imagine one player ($M=1$) running \MCTopM{} with the false knowledge of $M'=2$, and if it learned to accurately identify the set of the $2$ best arms, then the \MCTopM{} orthogonalization scheme can make it play the worst of the two arms, and as $M=1$ this player will never encounter any collision, thus playing this sub-optimal arm for about $T-\bigO{\log(T)}$ times, also leading to linear regret.

@@

We consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and a horizon of $T=10000$.
As before, we include the centralized multiple-play \klUCB{} as an unachievably efficient baseline, the \Selfish-\klUCB{} algorithm as an heuristic which does not require to know $M$.
Then we compare the \RhoRand, \RandTopM{} and \MCTopM{} algorithms, using \klUCB, which know $M$ beforehand, with their extensions implementing the same algorithm as \rhoRandEst, to estimate $M$ on the fly.

@@

The recent work \cite{BoursierPerchet18} proposed an idea they called the ``communication trick''.
It essentially allow any player to send one bit to all the others, at some pre-agreed time steps, with no modification on the model.
Thanks to this ``communication trick'', recent research efforts have been more focus on studying the basic model --without explicit communications between players--, while proposing algorithms that can rely on some communication between players.
This trick essentially use the fact that the players share a synchronized time, thus they can use a collision as a way to directly exchange one bit of information between two players.
This process is slow and not efficient, as all but two players must do nothing when player $i$ is sending a bit to player $j$, but it does build a communication protocol in the model without explicit communication between players.
This ``communication trick'' is used for instance in \cite{KaufmannAbbas19}.
We let the interested reader refer to these last two works \cite{BoursierPerchet18,KaufmannAbbas19} as they are both solid, and well explained.

@@

To illustrate the difficulty of the ``no sensing'' case, we illustrate here the performances of different algorithms designed specifically for this setting.
As above, we consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $N=100$ independent repetitions, and horizon $T=10000$.
We include the \Selfish-\klUCB{} algorithm as an heuristic, as well as the Improved \MusicalChair{} algorithm from \cite{LugosiMehrabian18} and \textsc{Sic-MMAB} from \cite{BoursierPerchet18}.
It is also interesting to add the centralized multiple-play \klUCB{} is included as an unrealistic efficient baseline, as it does not use the sensing information but only the joint information (the reward) $r^j(t)$, because it directly affects the player in an orthogonal configuration and thus never encounters any collision (thus $r^j(t)=Y_{t,A^j(t)}$ for each $j,t$).
%
For the two other algorithms, we use the advised tuning of their parameters:
for \textsc{Sic-MMAB}, we used $T_0 = \lceil K \log(T) \rceil$,
% as advised by the authors.
for Improved-MC, we used $c=1$ which gives $g=235$, whereas in the paper the authors use $c=128$ for their analysis.
We found empirically no difference when using different values of the constant $c$ or $g$, and unfortunately the regret of Improved-MC was always found to be linear\footnote{~For instance Improved-MC obtained a mean regret $12150$ for $T=10000$, for $M=3,K=9$, but seeing one value for one horizon does not mean anything, and we also experimented with larger values of $T$ and found a similar linear behavior.}.

@@

Moreover, at first sight, this idea of ``meta'' arms implies an exponential blow up in terms of computational and storage cost, as there is ${M \choose K}$ such ``meta arms'', but
the authors provide in Section~4.1 and Lemma~4.1 \cite{AlaturLevyKrause19} an interesting discussion regarding the time efficiency of their proposed algorithm, and they show it can stay polynomial in $M$ and $K$ by leveraging techniques from the Determinental Point Processes (DPP, see \cite{GaBaVa18} and references therein for a good introduction).
%
In this second work also, we can note the poor experimental section, as the proposed algorithm is only compared against the \MusicalChair{} algorithm, in ``easy'' problems (small number of break-points $\Upsilon_T$).
Despite being more complicated than other approaches, their algorithm ``\texttt{C \& P}'' should not be too hard to implement by ourselves, and studying its empirical performance is an interesting future work.

>>>>

\paragraph{Performance of our proposals for a wrong value of $M$.}
\label{par:5:usingWrongValueofM}
%
We can start by asking whether the most efficient algorithm, \MCTopM-\klUCB, is still efficient if it uses a value $M'$ different from the real number of players $M$.
Even though we did not include numerical simulations for this case in Section~\ref{sec:5:experiments} above, we did some tests, which confirmed two disappointing results that were also proven analytically.
First, the three algorithms (\RhoRand, \RandTopM{} and \MCTopM) give linear regret if they are using a value $M'$ strictly smaller than $M$ (and if $\mu^*_{M-1} > \mu^*_M$), as players will converge to play about $T-\bigO{\log(T)}$ times the $M-1$ best arms, leading to at least one collision most of the time, and thus a linear regret.
Second, if the $M$ players falsely use a value $M' > M$, then there is also a certain (fixed) probability to achieve a linear regret. Indeed, imagine one player ($M=1$) running \MCTopM{} with the false knowledge of $M'=2$, and if it learned to accurately identify the set of the $2$ best arms, then the \MCTopM{} orthogonalization scheme can make it play the worst of the two arms, and as $M=1$ this player will never encounter any collision, thus playing this sub-optimal arm for about $T-\bigO{\log(T)}$ times, also leading to linear regret.

@@

We consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $100$ independent repetitions and a horizon of $T=10000$.
As before, we include the centralized multiple-play \klUCB{} as an unachievably efficient baseline, the \Selfish-\klUCB{} algorithm as a heuristic which does not require to know $M$.
Then we compare the \RhoRand, \RandTopM{} and \MCTopM{} algorithms, using \klUCB, which know $M$ beforehand, with their extensions implementing the same algorithm as \rhoRandEst, to estimate $M$ on the fly.

@@

The recent work \cite{BoursierPerchet18} proposed an idea they called the ``communication trick''.
It essentially allow any player to send one bit to all the others, at some pre-agreed time steps, with no modification on the model.
Thanks to this ``communication trick'', recent research efforts have been more focus on studying the basic model --without explicit communications between players--, while proposing algorithms that can rely on some communication between players.
This trick essentially use the fact that the players share a synchronized time, thus they can use a collision as a way to directly exchange one bit of information between two players.
Such process is slow and not efficient, as all but two players must do nothing when player $i$ is sending a bit to player $j$, but it does build a communication protocol in the model without explicit communication between players.
We note that this ``communication trick'' is used for instance in \cite{KaufmannAbbas19},
and we let the interested reader refer to these two recent works \cite{BoursierPerchet18,KaufmannAbbas19}.
%  as they are both solid, and well explained.

@@

To illustrate the difficulty of the ``no sensing'' case, we illustrate here the performances of different algorithms designed specifically for this setting.
As above, we consider a bandit problem with $K=9$ arms, of means $0.1,\dots,0.9$, and three different cases of $M=3,6,9$ players, for $N=100$ independent repetitions, and horizon $T=10000$.
We include the \Selfish-\klUCB{} algorithm as a heuristic, as well as the Improved \MusicalChair{} algorithm from \cite{LugosiMehrabian18} and \textsc{Sic-MMAB} from \cite{BoursierPerchet18}.
It is also interesting to add the centralized multiple-play \klUCB{} is included as an unrealistic efficient baseline, as it does not use the sensing information but only the joint information (the reward) $r^j(t)$, because it directly affects the player in an orthogonal configuration and thus never encounters any collision (thus $r^j(t)=Y_{t,A^j(t)}$ for each $j,t$).
%
For the two other algorithms, we use the advised tuning of their parameters:
for \textsc{Sic-MMAB}, we used $T_0 = \lceil K \log(T) \rceil$,
% as advised by the authors.
for Improved-MC, we used $c=1$ which gives $g=235$, whereas in the paper the authors use $c=128$ for their analysis.
We found empirically no difference when using different values of the constant $c$ or $g$, and unfortunately the regret of Improved-MC was always found to be linear\footnote{~For instance Improved-MC obtained a mean regret $12150$ for $T=10000$, for $M=3,K=9$, but seeing one value for one horizon does not mean anything, and we also experimented with larger values of $T$ and found a similar linear behavior.}.

@@

Moreover, at first sight, this idea of ``meta'' arms implies an exponential blowup in terms of computational and storage cost, as there is ${M \choose K}$ such ``meta arms'', but
the authors provide in Section~4.1 and Lemma~4.1 \cite{AlaturLevyKrause19} an interesting discussion regarding the time efficiency of their proposed algorithm, and they show it can stay polynomial in $M$ and $K$ by leveraging techniques from the Determinental Point Processes (DPP, see \cite{GaBaVa18} and references therein for a good introduction).
%
In this second work also, we can note the poor experimental section, as the proposed algorithm is only compared against the \MusicalChair{} algorithm, in ``easy'' problems (small number of break-points $\Upsilon_T$).
Despite being more complicated than other approaches, their algorithm ``\texttt{C \& P}'' should not be too hard to implement by ourselves, and studying its empirical performance is an interesting future work.

### 2019-07-10 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Last pass with http://emccabedj.ucc.asn.au/checktex.html

Note than when a break-point occurs, we do not assume that all the arms means  change, but that \emph{there exists} an arm whose mean has changed.
Depending on the application, many scenario can be meaningful: changes can occur on all arms simultaneously (due to some exogenous event), or only one or a few arms change at each break-point.
For instance, for a cognitive radio application in a IoT-like network, we can imagine that all the devices of one company (or network provider) use a fixed (or a subset of) channel(s), and on a particular day in a city, if the company deploys a lot of new devices, then one (or some) channel(s) see their mean occupancy rates abruptly change.

@@

Then, we compare our algorithms to several competitors designed for a piece-wise stationary model. For a fair comparison, all algorithms that use  \UCB{} as a sub-routine were adapted to use \klUCB{} instead, which yields better performance\footnote{\cite{LiuLeeShroff17,CaoZhenKvetonXie18} both mention that extending their analysis to the use of \klUCB{} should not be too difficult.}. Moreover, all the algorithms are tuned as described in the corresponding paper, using in particular the knowledge of the number of break-points $\Upsilon_T$ and the horizon $T$. We first include three \emph{passively adaptive algorithms}:
Discounted \klUCB{} (D-\klUCB, \cite{Kocsis06}), with discount factor $\gamma = 1 - \sqrt{\Upsilon_T/T}/4$, Sliding-Window \klUCB{} (SW-\klUCB,  \cite{Garivier11UCBDiscount}) using window-size $\tau = 2 \sqrt{T\log(T)/\Upsilon_T}$ and Discounted Thompson sampling (DTS, \cite{RajKalyani17}) with discount factor $\gamma = 0.95$. For this last algorithm, the discount factor $\gamma=0.75$ suggested by the authors was performing significantly worse on the problem instances we tried.
More precisely, we found that $\gamma\leq0.95$ gives better performances for short-term problems (problems $1,2,4$) and $\gamma\geq0.95$ is better suited for long experiments (problems $3,5$).
%
% \TODOE{Tu confirmes bien que $\gamma=0.75$ ne marchait sur AUCUN problème ? Car ta phrase actuelle n'exclut pas que ce choix marche pour les probèmes courts}
%
Additionally, we include the \ExpThreeS{} algorithm from \cite{Auer02NonStochastic}, setting its parameters as in the Corollary~8.3 of the paper: $\omega=1/T$ and $\gamma = \min(1, \sqrt{K (\Upsilon_T \log(KT) + \e) / ((\e-1)T)})$, based on a prior knowledge of $T$ and $\Upsilon_T$.

>>>>

Note than when a break-point occurs, we do not assume that all the arms means  change, but that \emph{there exists} an arm whose mean has changed.
Depending on the application, many scenarios can be meaningful: changes can occur on all arms simultaneously (due to some exogenous event), or only one or a few arms change at each break-point.
For instance, for a cognitive radio application in a IoT-like network, we can imagine that all the devices of one company (or network provider) use a fixed (or a subset of) channel(s), and on a particular day in a city, if the company deploys a lot of new devices, then one (or some) channel(s) see their mean occupancy rates abruptly change.

@@

Then, we compare our algorithms to several competitors designed for a piece-wise stationary model. For a fair comparison, all algorithms that use  \UCB{} as a sub-routine were adapted to use \klUCB{} instead, which yields better performance\footnote{~\cite{LiuLeeShroff17,CaoZhenKvetonXie18} both mention that extending their analysis to the use of \klUCB{} should not be too difficult.}. Moreover, all the algorithms are tuned as described in the corresponding paper, using in particular the knowledge of the number of break-points $\Upsilon_T$ and the horizon $T$. We first include three \emph{passively adaptive algorithms}:
Discounted \klUCB{} (D-\klUCB, \cite{Kocsis06}), with discount factor $\gamma = 1 - \sqrt{\Upsilon_T/T}/4$, Sliding-Window \klUCB{} (SW-\klUCB,  \cite{Garivier11UCBDiscount}) using window-size $\tau = 2 \sqrt{T\log(T)/\Upsilon_T}$ and Discounted Thompson sampling (DTS, \cite{RajKalyani17}) with discount factor $\gamma = 0.95$. For this last algorithm, the discount factor $\gamma=0.75$ suggested by the authors was performing significantly worse on the problem instances we tried.
More precisely, we found that $\gamma\leq0.95$ gives better performances for short-term problems (problems $1,2,4$) and $\gamma\geq0.95$ is better suited for long experiments (problems $3,5$).
%
% \TODOE{Tu confirmes bien que $\gamma=0.75$ ne marchait sur AUCUN problème ? Car ta phrase actuelle n'exclut pas que ce choix marche pour les probèmes courts}
%
Additionally, we include the \ExpThreeS{} algorithm from \cite{Auer02NonStochastic}, setting its parameters as in the Corollary~8.3 of the paper: $\omega=1/T$ and $\gamma = \min(1, \sqrt{K (\Upsilon_T \log(KT) + \e) / ((\e-1)T)})$, based on a prior knowledge of $T$ and $\Upsilon_T$.

### 2019-07-10 3-Appendices/2-Appendix/Revisiting_Doubling_Trick_for_Multi-Armed_Bandits.git/Revisiting_Doubling_Trick_for_Multi-Armed_Bandits.tex
Using \begin{framed}...\end{framed} for all algorithms.
New references. I need to finish Ch1 and Ch2
Last pass with http://emccabedj.ucc.asn.au/checktex.html

\todo[inline]{begin todo}
    \begin{itemize}
        \item
        Change the motivation:
        understanding why those doubling tricks are used, and what they can preserve...
        \item
        Remove the idea of problem dependent + worse-case optimal
        \item
        Update the literature review:
        Talk about the \KLUCBswitch{} algorithm from \cite{Garivier18}.
    \end{itemize}
\todo[inline]{end todo}

@@

% Outline of this article
%\paragraph{Outline}
The rest of the paper is organized as follows.
The Doubling Trick is formally defined in Section~\ref{sec:genericAlgo}, along with a generic tool for its analysis.
In Section~\ref{sec:geometricDoublingTrick}, we present upper and lower bounds on the regret of algorithms to which a geometric Doubling Trick is applied.
Section~\ref{sec:exponentialDoublingTrick} investigates regret guarantees that can be obtained for a ``faster'' exponential Doubling Trick.
Experimental results are then reported in Section~\ref{sec:experiments}.
Complementary elements of proofs are deferred to the appendix.
% We give missing proofs and additional results in Appendix~\ref{sec:missingproofs}, an heuristic $\DTnr$ improving $\DTr$ in App.~\ref{sec:DTnr} along with more experimental results in App.~\ref{sec:otherExperiments}, and other technical tools are given in App.~\ref{sec:otherproofs}.

@@

\vspace*{5pt}  % XXX remove if problem
% \centering
% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
% \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
\begin{algorithm}[H]
        % XXX Options
        \LinesNumbered  % XXX Option to number the line
        \DontPrintSemicolon
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{Bandit algorithm $\cA$, and doubling sequence $(T_i)_{i\in\N}$.}
        % \KwData{Data}
        % \KwResult{Result}
        \BlankLine
        % XXX Algorithm
        Let $i = 0$, and initialize algorithm $\cA^{(0)} = \cA_{T_0}$.\;
        \For{$t = 1, \dots, T-1$}{
            \If(\tcp*[f]{Next horizon $T_{i+1}$ from the sequence}){
                $t > T_i$
            }{
                Let $i = i + 1$.\;
                Initialize algorithm $\cA^{(i)} = \cA_{T_i - T_{i-1}}$.
                \tcp*[f]{Full restart}
            }
            Play with $\cA^{(i)}$: play arm $A'(t) := A^{(i)}(t - T_{i-1})$, observe reward $r(t) = Y_{A'(t), t}$. \nllabel{line:internalTimer_DTr}
        }
        \caption{The Generic Doubling Trick Algorithm, $\cA' = \DTr(\cA, (T_i)_{i\in\N})$.}
\label{algo:DTr}
\end{algorithm}
% \vspace*{-5pt}  % XXX remove if problem
\vspace*{5pt}  % XXX remove if problem

@@

We first provide some details on these two algorithms, and then illustrate the behavior of Doubling Tricks applied to these algorithms with different doubling sequences.
% \cite{Garivier18}

@@

Another version of the Doubling Trick with ``no restart'', denoted $\DTnr$, is presented in Appendix~\ref{sec:DTnr}, but it is only an heuristic and cannot be applied to any algorithm $\cA$.
Algorithm~\ref{algo:DTnr} can be applied to \KLUCBpp{} or \AFHG{} for instance, as they use $T$ just as a numerical parameter (see Eqs.~\ref{eq:index_AFHG} and \ref{eq:index_KLUCBpp}), but its first limitation is that it cannot be applied to \DMEDp{} \citep{Honda10} or \Exppp{} \citep{Seldin17}, or any algorithms based on arm eliminations, for example.
%
A second limitation is the difficulty to analyze this ``no restart'' variant,
due to the unpredictable effect on regret of giving non-uniform prior information to the underlying algorithm $\cA$ on each successive sequence.
An interesting future work would be to analyze it, either in general or for a specific algorithm like \KLUCBpp.
%
Despite its limitations, this heuristic exhibits as expected better empirical performance than \DT, as can be observed in Appendix~\ref{sec:otherExperiments}.

@@

\vspace*{5pt}  % XXX remove if problem
% \centering
% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
% \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
\begin{algorithm}[H]
        % XXX Options
        \LinesNumbered  % XXX Option to number the line
        \DontPrintSemicolon
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{Bandit algorithm $\cA$, and sequence $(T_i)_{i\in\N}$\;}
        % \KwData{Data}
        % \KwResult{Result}
        \BlankLine
        % XXX Algorithm
        Let $i = 0$, and initialize algorithm $\cA^{(0)} = \cA_{T_0}$.\\
        \For{$t = 1, \dots, T$}{
            \If(\tcp*[f]{Next horizon $T_{i+1}$ from the sequence}){
                $t > T_i$
            }{
                Let $i = i + 1$.\;
                Initialize algorithm $\cA^{(i)} = A_{T_i - T_{i-1}}$.\;
                Update internal memory of $\cA^{(i)}$ with the history of plays and rewards from $\cA_{i-1}$.
            }
            Play with $\cA^{(i)}$: play arm $A'(t) := A^{(i)}(t - T_i)$, observe reward $r(t) = Y_{A'(t), t}$. \nllabel{line:internalTimer_DTnr}
        }
        \caption{The Non-Restarting Doubling Trick Algorithm, $\cA' = \DTnr(\cA, (T_i)_{i\in\N})$.}
\label{algo:DTnr}
\end{algorithm}
% \vspace*{-5pt}  % XXX remove if problem
\vspace*{10pt}  % XXX remove if problem

@@

As mentioned previously, the \DTnr{} algorithm (Algorithm~\ref{algo:DTnr})
is only an heuristic so far, as no theoretical guarantee was proved for it.
%
For the sake of completeness, we also include results from numerical experiments with it, to compare its performance against the ``with restart'' version \DTr.

>>>>

\todo[inline]{begin todo}
    \begin{itemize}
        \item
        Change the motivation:
        understanding why those doubling tricks are used, and what they can preserve...
        \item
        Remove the idea of problem dependent + worse-case optimal
        \item
        Update the literature review:
        Talk about the \KLUCBswitch{} algorithm from \cite{GarivierHadiji2018}.
    \end{itemize}
\todo[inline]{end todo}

@@

% Outline of this article
%\paragraph{Outline}
The rest of the paper is organized as follows.
The Doubling Trick is formally defined in Section~\ref{sec:genericAlgo}, along with a generic tool for its analysis.
In Section~\ref{sec:geometricDoublingTrick}, we present upper and lower bounds on the regret of algorithms to which a geometric Doubling Trick is applied.
Section~\ref{sec:exponentialDoublingTrick} investigates regret guarantees that can be obtained for a ``faster'' exponential Doubling Trick.
Experimental results are then reported in Section~\ref{sec:experiments}.
Complementary elements of proofs are deferred to the appendix.
% We give missing proofs and additional results in Appendix~\ref{sec:missingproofs}, a heuristic $\DTnr$ improving $\DTr$ in App.~\ref{sec:DTnr} along with more experimental results in App.~\ref{sec:otherExperiments}, and other technical tools are given in App.~\ref{sec:otherproofs}.

@@

\vspace*{5pt}  % XXX remove if problem
% \centering
% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
% \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
\begin{framed}
\begin{algorithm}[H]
        % XXX Options
        \LinesNumbered  % XXX Option to number the line
        \DontPrintSemicolon
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{Bandit algorithm $\cA$, and doubling sequence $(T_i)_{i\in\N}$.}
        % \KwData{Data}
        % \KwResult{Result}
        \BlankLine
        % XXX Algorithm
        Let $i = 0$, and initialize algorithm $\cA^{(0)} = \cA_{T_0}$.\;
        \For{$t = 1, \dots, T-1$}{
            \If(\tcp*[f]{Next horizon $T_{i+1}$ from the sequence}){
                $t > T_i$
            }{
                Let $i = i + 1$.\;
                Initialize algorithm $\cA^{(i)} = \cA_{T_i - T_{i-1}}$.
                \tcp*[f]{Full restart}
            }
            Play with $\cA^{(i)}$: play arm $A'(t) := A^{(i)}(t - T_{i-1})$, observe reward $r(t) = Y_{A'(t), t}$. \nllabel{line:internalTimer_DTr}
        }
        \caption{The Generic Doubling Trick Algorithm, $\cA' = \DTr(\cA, (T_i)_{i\in\N})$.}
\label{algo:DTr}
\end{algorithm}
\end{framed}
% \vspace*{-5pt}  % XXX remove if problem
\vspace*{5pt}  % XXX remove if problem

@@

We first provide some details on these two algorithms, and then illustrate the behavior of Doubling Tricks applied to these algorithms with different doubling sequences.
% \cite{GarivierHadiji2018}

@@

Another version of the Doubling Trick with ``no restart'', denoted $\DTnr$, is presented in Appendix~\ref{sec:DTnr}, but it is only a heuristic and cannot be applied to any algorithm $\cA$.
Algorithm~\ref{algo:DTnr} can be applied to \KLUCBpp{} or \AFHG{} for instance, as they use $T$ just as a numerical parameter (see Eqs.~\ref{eq:index_AFHG} and \ref{eq:index_KLUCBpp}), but its first limitation is that it cannot be applied to \DMEDp{} \citep{Honda10} or \Exppp{} \citep{Seldin17}, or any algorithms based on arm eliminations, for example.
%
A second limitation is the difficulty to analyze this ``no restart'' variant,
due to the unpredictable effect on regret of giving non-uniform prior information to the underlying algorithm $\cA$ on each successive sequence.
An interesting future work would be to analyze it, either in general or for a specific algorithm like \KLUCBpp.
%
Despite its limitations, this heuristic exhibits as expected better empirical performance than \DT, as can be observed in Appendix~\ref{sec:otherExperiments}.

@@

\vspace*{5pt}  % XXX remove if problem
% \centering
% Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
% Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
% \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
\begin{framed}
\begin{algorithm}[H]
    % XXX Options
    \LinesNumbered  % XXX Option to number the line
    \DontPrintSemicolon
    % \RestyleAlgo{boxed}
    % XXX Input, data and output
    \KwIn{Bandit algorithm $\cA$, and sequence $(T_i)_{i\in\N}$\;}
    % \KwData{Data}
    % \KwResult{Result}
    \BlankLine
    % XXX Algorithm
    Let $i = 0$, and initialize algorithm $\cA^{(0)} = \cA_{T_0}$.\\
    \For{$t = 1, \dots, T$}{
        \If(\tcp*[f]{Next horizon $T_{i+1}$ from the sequence}){
            $t > T_i$
        }{
            Let $i = i + 1$.\;
            Initialize algorithm $\cA^{(i)} = A_{T_i - T_{i-1}}$.\;
            Update internal memory of $\cA^{(i)}$ with the history of plays and rewards from $\cA_{i-1}$.
        }
        Play with $\cA^{(i)}$: play arm $A'(t) := A^{(i)}(t - T_i)$, observe reward $r(t) = Y_{A'(t), t}$. \nllabel{line:internalTimer_DTnr}
    }
    \caption{The Non-Restarting Doubling Trick Algorithm, $\cA' = \DTnr(\cA, (T_i)_{i\in\N})$.}
\label{algo:DTnr}
\end{algorithm}
\end{framed}
% \vspace*{-5pt}  % XXX remove if problem
\vspace*{10pt}  % XXX remove if problem

@@

As mentioned previously, the \DTnr{} algorithm (Algorithm~\ref{algo:DTnr})
is only a heuristic so far, as no theoretical guarantee was proved for it.
%
For the sake of completeness, we also include results from numerical experiments with it, to compare its performance against the ``with restart'' version \DTr.

### 2019-07-10 5-Nomenclature/Nomenclature.tex
Last pass with http://emccabedj.ucc.asn.au/checktex.html

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_k^{(i)}$}{Mean of arm $k$, arm $k$ at time $t$ (in Chapter~\ref{chapter:6}), arm $k$ for user $j$ (in Chapter~\ref{chapter:5}), arm $k$ in the $i$-th stationary interval (in Chapter~\ref{chapter:6})}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda},$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps ($\Delta^{\text{opt}}$ and $\Delta^{\text{change}}$)}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known beforehandby an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau_k^{(i)}$}{Location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, the parameter for the $\varepsilon$-greedy algorithm, or the drift correction parameter for \CUSUM{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}}
\nomenclature[G]{$\omega$}{Denotes a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta(n,\delta)$}{Usually denotes a threshold for the statistical (GLR) tests in Chapter~\ref{chapter:6}}

>>>>

% --------------------------------
% matches Greek Symbols        > G
\nomenclature[G]{$\nu_k$, $\nu_k(t)$, $\nu_k^j$}{Distribution of arm $k$, arm $k$ at time $t$, arm $k$ for user $j$}
\nomenclature[G]{$\mu_k$, $\mu_k(t)$, $\mu_k^j$, $\mu_k^{(i)}$}{Mean of arm $k$, arm $k$ at time $t$ (in Chapter~\ref{chapter:6}), arm $k$ for user $j$ (in Chapter~\ref{chapter:5}), arm $k$ in the $i$-th stationary interval (in Chapter~\ref{chapter:6})}
\nomenclature[G]{$\mu^*$, $\mu_k^*$}{Mean of the optimal arm (\ie, $\mu^*=\max_k \mu_k$), and mean of the $k$-th best arm}
\nomenclature[G]{$\bm{\mu},\bm{\nu},\bm{\lambda}$}{Vector of means $(\mu_k) = \mu_1,\dots,\mu_K$, or vector of distributions $(\nu_k)_k$ or $(\lambda_k)_k$ (characterizing a problem)}
\nomenclature[G]{$\Delta$}{Usually denotes the gap in terms of means of arms, usually between the best and second best arms, in Chapters~\ref{chapter:2}, \ref{chapter:5}. In Chapter~\ref{chapter:4} in Algorithm~\ref{algo:43:UCBwithDelay} it denotes a delay. In Chapter~\ref{chapter:6}, it can denote different gaps ($\Delta^{\text{opt}}$ and $\Delta^{\text{change}}$)}
\nomenclature[G]{$\Delta n$, $\Delta s$}{Parameters of numerical optimization tricks in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\delta$}{Usually denotes a lower-bound on the gap $\Delta$, known beforehandby an algorithm, in Chapters~\ref{chapter:5}, \ref{chapter:6}. Also denote a confidence level of an algorithm in Section~\ref{sec:6:ChangePointDetector}}
\nomenclature[G]{$\Upsilon_T$}{Number of break-points in a piece-wise stationary MAB problem in Chapter~\ref{chapter:6}. $\NCi$ denotes the number of change-points on arm $i$, and $C_T = \sum_{i=1}^{K} \NCi$ the number of change-points on the arms}
\nomenclature[G]{$\tau_k^j$, $\tau_k^{(i)}$}{Location of a change-point, \eg, the $j$-th change-point on arm $k$, in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\tau$}{Length of a sliding-window, \eg, in SW-\UCB{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\gamma$}{Usually denotes a discount factor, \eg, in D-\UCB{} or D-TS in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\varepsilon$}{Usually denotes a small positive real value, \eg, the parameter for the $\varepsilon$-greedy algorithm, or the drift correction parameter for \CUSUM{} in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\alpha$}{Denotes the parameter of a \UCB{} algorithm in Chapters~\ref{chapter:2} and \ref{chapter:4}}
\nomenclature[G]{$\omega$}{Denotes a parameter controlling the forced exploration mechanism in Chapter~\ref{chapter:6}}
\nomenclature[G]{$\beta(n,\delta)$}{Usually denotes a threshold for the statistical (GLR) tests in Chapter~\ref{chapter:6}}
